### 2023-09-13 main.tex
abs-check
sdfg
lkj

\textbf{Remark}: Using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as 
\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=&\sum_{c_{1},\ldots,c_{m}=0}^{1}

@@

=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{q}^{t_{q}}\beta_{q}^{1-t_{q}}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})

@@

Using formula \eqref{ABS} for a configuration where all $\tau_{i}$ are non-empty species, we obtain that 
	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}

@@

The above matrices satisfy

@@

Arguing as in section \ref{SectionNonLocalTrasformation} and using the resolvent operator of $Q_{2L}$ with eigenvalues $\Lambda_{m}$, one can show that 

@@

	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{m}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{m}+\epsilon-Q^{2L}_{0}-\mathcal{Q}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|

@@

		\lim_{\epsilon\to0}\sum_{m=0}^{L}\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|

@@

		&\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\left((\lambda_{m}+\epsilon)-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\sum_{n=0}^{\infty}\left((\Lambda_{m}+\epsilon)^{-1}Q_{0}^{2L}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}B_{1}^{2L-1}\right\}^{k}\\

@@

		W|\Psi_{m}^{0}\rangle=&\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}

@@

		W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\lambda_{m}^{Q}+\epsilon)-\Lambda_{m}^{Q}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}

>>>>

\textbf{Remark}: using binomial theorem we rewrite the \eqref{exactCorrelations} as 
\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=&
\sum_{c_{1},\ldots,c_{m}=0}^{1}
f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})\right)\\
=&\sum_{c_{1},\ldots,c_{m}=0}^{1}

@@

=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{q}^{t_{q}}\beta_{q}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})

@@

Using formula \eqref{ABS} for a configuration where all $\tau_{x_{i}}=a_{i}$  for $i=1,\ldots,m$ and $\tau_{j}=N$ for $j\in\{1,\ldots,L\}\setminus \{x_{1},\ldots,x_{m}\}$, we obtain 
 \langle\hat{\bm{\xi}}\rangle_{stat,dual}=\Psi^{''}(\tau_{1},\ldots,\tau_{L})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,x_{k},c_{k},\ldots,c_{m})$ we have \eqref{exactCorrelations}.

@@

The above matrices satisfy:

@@

Arguing as in section \ref{SectionNonLocalTrasformation} and using the resolvent operator of $Q_{2L}$ with eigenvalues $\Lambda_{\bm{m}}$, one can show that 

@@

	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}_{0}-\mathcal{Q}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|

@@

		\lim_{\epsilon\to0}\sum_{m=0}^{L}\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|

@@

		&\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\left((\Lambda_{m}+\epsilon)-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\sum_{n=0}^{\infty}\left((\Lambda_{m}+\epsilon)^{-1}Q_{0}^{2L}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}B_{1}^{2L-1}\right\}^{k}\\

@@

		W|\Psi_{m}^{0}\rangle=&\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-Q_{0}^{2L}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}

@@

		W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-\Lambda_{m}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
